### 2021-03-21 paper/linkagecluster_bk_paper.Rmd
hashing is awesome

However, if we want to ensure the theoretic purity of each MCMC sample of the linkage structure, we can "recouple" $\mathbf{Z}$ by simply resolving these illegal matchings. Explictly, define clusters $R(i) := \{j | Z_j = i\}$, and define all clusters such that $|R(i)| > 1$ as *resolution clusters*.  Within each cluster, resample the candidate matches according to their Fellegi-Sunter weights. We show this step to be computationally inexpensive and to be a reasonable replication of more organic one-to-one matching. This procedure would be most useful in cases where there are many "near matches" across files, but in most cases, we find this this step to be unnecessary.

>>>>

However, if we want to ensure the theoretic purity of each MCMC sample of the linkage structure, we can "recouple" $\mathbf{Z}$ by simply resolving these illegal matchings. Explictly, define sets $R(i) := \{j | Z_j = i\}$, and define all sets such that $|R(i)| > 1$ as *resolution sets*.  Within each set, resample the candidate matches according to their Fellegi-Sunter weights. We show this step to be computationally inexpensive and to be a reasonable replication of more organic one-to-one matching. This procedure would be most useful in cases where there are many "near matches" across files, but in most cases, we find this this step to be unnecessary.
